Selecting and Controlling Physical Devices Through a Head-Mounted Display with Infrared Targeting

### 2013-09-02 doc/sigchi14/device.tex
bjoern's pass at overall narrative

@@

Our prototype consists of a Google Glass Explorer Edition head-worn computing device, augmented with an infrared emitter that is mounted on the frame, pointing out in the direction of the wearer's view (Figure~\ref{fig:glass}). The IR emitter LED is mounted in an opaque hollow tube, that restricts the outgoing angle of illumination. The angle can be adjusted by moving the LED in or out of the tube.

@@

In our prototype, Glass communicates over Bluetooth to an additional microcontroller PCB the user has to wear. This board marshals XBee to Bluetooth messages in both directions and also controls the IR LED mounted on the Glass frame. This architecture was mostly chosen for reasons of expediency. Future headmounted devices could clearly integrate IR emitters; the choice of local area wireless technology could also change . \bjoern{why not all bluetooth? There's probably a pairing/latency argument to be made here.}

\subsection{Device Characterization}
We characterized the usable range and selection accuracy... (see Figure~\ref{fig:coverage} and Table~\ref{table:measurements}).
\bjoern{insert text from google doc here}

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/glass-with-ir}
\caption{Our augmented Glass prototype has a frame-mounted infrared emitter.}
\label{fig:glass}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/glass-with-ir}
\caption{Our augmented Glass prototype has a frame-mounted infrared emitter.}
\label{fig:glass}
\end{figure}
\begin{figure}[t]
\centering
\includegraphics[width=1.0\columnwidth]{figures/architecture}
\caption{System architecture.}
\label{fig:architecture}
\end{figure}

@@

Our prototype consists of a Google Glass Explorer Edition head-worn computing device, augmented with an infrared emitter that is mounted on the frame, pointing out in the direction of the wearer's view (Figure~\ref{fig:glass}). The IR emitter LED is mounted in an opaque hollow tube, that restricts the outgoing angle of illumination.

@@

In our prototype, Glass communicates over Bluetooth to an additional microcontroller PCB the user has to wear (Atmel ATMega256). This board marshals XBee to Bluetooth messages in both directions and also controls the IR LED mounted on the Glass frame (Figure~\ref{fig:architecture}). This architecture was mostly chosen for reasons of expediency. We selected XBee 802.15.4 radios to avoid the latency associated with connecting and disconnecting to Bluetooth devices \bjoern{Is this true or not?} Future head-mounted devices could clearly integrate IR emitters; the choice of local wireless technology could also change. In particular, one could substitute WiFi modules.

\subsection{Device Characterization}
We determined the usable range and accuracy empirically with one IR emitter and two IR receivers. The IR emitter constantly sent out an id signal. The receivers that correctly received the signal turn their LED on for 300 ms.

We placed all three devices at the same height with clear line of sight. The IR emitter is first places 2 feet away from the receivers. The receivers were moved sideways apart from each other until they could no longer receive stable signals. We then recorded the distance of the two receivers for the calculation of coverage angles. The steps are repeated for IR emitters in different distances (as shown in Table~\ref{table:measurements}). We then repeated measurements with the emitter  placed at various depths in the tube (see Figure~\ref{fig:coverage}).

In summary, \bjoern{describe what the measured results mean in practice.}

### 2013-09-02 doc/sigchi14/introduction.tex
bjoern's pass at overall narrative

\section{Introduction}
\bjoern{What's the overall motivation for the project? What problem does it address?}
Increasingly, devices and services in our built environment such as intelligent lighting, televisions, HVAC systems, laundry machines, blinds or kitchen appliances are networked and can be controlled remotely.

The proliferation of smart, controllable devices raises the question of how to best interact with them. Prior work has introduced several approaches that use handheld mobile devices as {\em universal remote controls} to select and control appliances in the proximate environment- e.g., through pointing at such devices to select them, and through touch-screen or button interfaces to send control commands~\cite{}. Commercial universal control applications for smart phones are also available~\cite{}, though they usually do not offer spatial selection of target devices, forcing users to browse through lists of configured devices instead.

\bjoern{what are the drawbacks of this existing work?}
Some drawbacks of using handheld devices are that the device first has to be retrieved (e.g., from a pocket) and aimed; that two hands may be necessary for operation (one to hold the device, one to operate the touch screen); and that the user's visual attention is split between looking down at a screen and out at the device to-be-controlled. \bjoern{these all sound kind of weak.} These general limitations have led researchers to investigate ``always-available'' physiological input modalities on one hand~\cite{saponas}, and wearable computing devices~\cite{} on the other hand.

>>>>

\section{Introduction}
\bjoern{What's the overall motivation for the project? What problem does it address?}
Increasingly, devices and services in our built environment are networked and can be controlled remotely. The proliferation of smart, controllable devices such as intelligent lighting, AV equipment, HVAC systems, or kitchen appliances raises the question of how to best interact with them. Prior work has introduced several approaches that use handheld mobile devices as {\em universal remote controls} to select and control appliances in the proximate environment- e.g., through pointing at such devices to select them, and through touch-screen or button interfaces to send control commands~\cite{beigl_point_1999,patel_2-way_2003}.

\bjoern{what are the drawbacks of this existing work?}
Some drawbacks of using handheld devices are that the device first has to be retrieved (e.g., from a pocket) and aimed; that two hands may be necessary for operation (one to hold the device, one to operate the touch screen); and that the user's visual attention is split between looking down at a screen and out at the device to-be-controlled. \bjoern{these all sound kind of weak.} These general limitations have led researchers to investigate ``always-available'' physiological input modalities for phones on one hand~\cite{morris_emerging_2011}, and wearable computing devices on the other hand.
